% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Aditya Komawar}

\basicInfo{
  \marker{Pune - 411041}
  }

\basicInfo{
  \email{adityakomawar7@gmail.com} \textperiodcentered\ 
  \phone{+91 9881211077} \textperiodcentered\ 
  \linkedin[aditya-komawar-535396184]{https://www.linkedin.com/in/aditya-komawar-535396184/}}

\section{Education}
\datedsubsection{\textbf{Smt. Kashibai Navale College of Engineering}}{2018 -- 2022}
\datedline{\textit{Bachelor of Engineering in Information Technology (CGPA - 9.03/10)}} {Pune}
\datedsubsection{\textbf{Taywade Jr. College}}{2018}
\datedline{\textit{HSC (67.08\%)}} {Nagpur}
\datedsubsection{\textbf{Z. P. High School}}{2016}
\datedline{\textit{SSC (81.60\%)}} {Pandharkawada - 445302}

\section{Experience}

\datedsubsection{\textbf{Persistent Systems} Pune}{June 2022 -- Present}
\role{Software Engineer}{}
% Brief introduction: Java Full Stack Engineer
 \begin{itemize}
   \item Solved priority based Jira tickets for React Developement of client Project.
 \end{itemize}

\datedsubsection{\textbf{Persistent Systems (Internship)} Pune}{Jan 2022 -- June 2022}
\role{Software Engineer Intern}{}
% Brief introduction: Java Full Stack Engineer
 \begin{itemize}
   \item Java Full Stack - Completed mini project in React and Spring Boot
 \end{itemize}

\datedsubsection{\textbf{Bitsmith Technologies (Internship)} Pune}{Apr 2021 -- Jan 2022}
\role{React Frontend Developer as Intern}{}
% Brief introduction: Worked on web technologies
\begin{itemize}
 \item React, HTML, CSS, JavaScript
 \item Done developement in Web Portal of Bitsmith Classroom - an ERP/LMS and a College Workspace
\end{itemize}

\section{Projects}
\datedsubsection{\textbf{Brain Tumor Detection and Classification using Deep Learning} }{Final Year Project}
\datedline{Data Science, Django, JavaScript}{\href{https://adityakomawar.github.io/BE-Project-Brain-Tumor-Detection-and-Classification/}{Website Link}}
\begin{itemize}
 \item Used pre-trained VGG-16 model for brain tumor detection and classification. Classified Brain Tumor MRI images in respective tumor types.
\end{itemize}

\datedsubsection{\textbf{Blogs} } {}
\datedline{Django Website for blogs}{\href{http://blogs4u.herokuapp.com/}{Website Link}}
\begin{itemize}
 \item A basic blogging website. User can view all existing blogs in reverse chronological order. Added authentication system. User can create new blog, edit user's existing blog.
\end{itemize}

\datedsubsection{\textbf{Football Transfer Market Management System} }{DBMS Mini Project}
\datedline{Java, JDBC, Java Swing}{\href{https://github.com/AdityaKomawar/dbms-mini-project}{Github Repo}}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C/C++, Python, JavaScript, Java
  \item Web Technologies: HTML, CSS, JavaScript, React, Django, Spring Boot
  \item Other: MySql, Git, Github, Jira, Tibco BWCE
\end{itemize}

%\section{Honors and Awards}
%\datedline{\textit Infytq Certification }{18 Apr. 2021}
%\datedline{-  PPO from Infosys}

\section{Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item \href{https://github.com/AdityaKomawar}{Github Profile} 
  \item \href{https://www.hackerrank.com/adityakomawar7}{HackerRank Profile} 
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
